Topic Modeling of News

### 2017-11-09 paper/R/02_combine.Rmd
add apis

# Extract FB Shares
```{r}
library(SocialMediaMineR)

facebook <- get_facebook(btw$url[1:100])

page <- readLines(paste0(check,btw$url[i]))

check <- "https://graph.facebook.com/?id="
pattern <- 'share_count\\":[0-9]+'

shares <- NULL

for (i in (length(shares)+1):nrow(btw)){
  page <- readLines(paste0(check,btw$url[i]))
  string <- str_extract(page, pattern)
  shares <- append(shares, as.numeric(str_extract(string, "[0-9]+")))
  Sys.sleep(10)
}
```

@@

```{r}
url_slice <- split(btw$url, ceiling(seq_along(btw$url)/1000))
file = "../output/urls"

for (i in 1:length(url_slice)){
  url = url_slice[[i]]
  count = as.character(i)
  write.table(url, file=paste0(file,count,".csv"), sep ="\n", 
              row.names = FALSE, quote = FALSE, col.names = FALSE)
}

write.table(urls1, file="../output/urls1.csv", sep ="\n", row.names = FALSE, quote = FALSE)
write.table(urls2, file="../output/urls2.csv", sep ="\n", row.names = FALSE, quote = FALSE)
```

```{r}
library(Rfacebook)

app_id = 1580533335373831
app_secret = "07ecdc314355649e13447278c57627f6"

shares
```

>>>>

# Extract FB Shares
```{r}
endpoint <- "https://api.sharedcount.com/?url="
api1 <- "&apikey=24abe04472f42e5003938b0314844010d6425d37"
api2 <- "&apikey=68d76247a02b3d39ff592aa5616ce9f73f182934"

pattern <- 'share_count\\":[0-9]+'
shares <- NULL

for (i in (length(shares)+1):nrow(btw)){
  page <- readLines(paste0(endpoint,btw$url[i],api2))
  string <- str_extract(page, pattern)
  shares <- append(shares, as.numeric(str_extract(string, "[0-9]+")))
}
```

```{r}
btw <- cbind(btw, shares)

btw.reg %>%
  filter(is.na(shares)) -> test
```

@@
